%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Project}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \paperentry
    {SGX-Shield: Enabling Address Space Layout Randomization for SGX Programs} % Role
    {} % Event
    {
        \begin{cvitems} % Description(s)
        \item {SGX-Shield is a system (compiler toolchains and runtime support)
            to enable ASLR (Address Space Layout Randomization) for SGX programs.}
        \item {Jaebaek Seo alone implemented all compiler toolchains including
                LLVM backends, static linker and dynamic loader/linker and runtime
            support including libraries and memory layout.}
        \item {The paper is still under review for publication.}
        \item {\url{https://github.com/jaebaek/SGX-Shield}}
        \end{cvitems}
    }

  \paperentry
    {FLEXDROID: Enforcing In-App Privilege Separation in Android} % Role
    {} % Date(s)
    {
        \begin{cvitems} % Description(s)
        \item {FlexDroid is an extension of Android permission system
            to support in-app privilege separation.}
        \item {Jaebaek Seo alone engineered memory permission part in kernel,
            Dalvik JVM, Android framework, dynamic loader/linker.}
        \item {\url{https://github.com/flexdroid}}
        \item {This work is published in Proceedings of the 2016 Network and
                Distributed System Security Symposium (\textbf{NDSS 2016},
                Acceptance ratio: 60/389=15.4\%).}
        \item {Jaebaek Seo is the first author of the paper.}
        \end{cvitems}
    }

  \paperentry
    {Optimal Real-Time Scheduling on Two-Type Heterogeneous Multicore Platforms} % Role
    {} % Date(s)
    {
        \begin{cvitems} % Description(s)
        \item {Jaebaek Seo contributed to prove mathmatical theorems.}
        \item{This work is published in Proceedings of the 36th IEEE Real-Time
                Systems Symposium (RTSS 2015, Acceptance ratio: 34/151=22.5\%)}
            \item {Jaebaek Seo is the second author of the paper.}
            \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
